Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-03 paper.tex
Item 30: Removed reference to 'Response of CPE in the footnote explaining the 64 second waittime'

In \cite{Cogan2008} it has been noted that results obtained using cyclic voltammetry are dependant on, among other factors, the measurement sweep rate. This indicates a lack of isolation between displacement and Faradaic mechanisms. Our measurements were repeated using wait-times of 4, 16, 32 and 64 seconds between voltage increments, allowing us to determine the effect of sweep rate. From these measurements and a separate investigation\footnote{A separate measurement of the response of the CPE to voltage increments is shown in figure~\ref{fig:CPE_currentVsTime}. We concluded that the measurement rate did not significantly affect results when using a wait-time of 64 seconds or greater when the applied voltage across both interfaces is beyond 0.7\thinspace V. These measurements were made in still solution and we expect that stirring will cause the CPE to come to equilibrium sooner. The wait time used between increments for this data was 10,000 seconds, of which only the first 250 seconds are shown. We believe these results give confidence to our assumption that a wait-time of 64 seconds is ``long enough''.} we concluded that a wait-time of 64 seconds was sufficient.
\begin{figure}
    \begin{center}
        \includegraphics{graphics/CPE_currentVsTime}
    \end{center}
    \caption{Current versus time after a stepped voltage increment across a pair of interfaces. Time before 64 seconds is highlighted in grey. Measurements were taken with a wait time of 10,000 seconds between increments.}
    \label{fig:CPE_currentVsTime}
\end{figure}

@@

11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
{\color{OliveGreen} 
    Item 30\\
    {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
    No response yet.
}\\

>>>>

In \cite{Cogan2008} it has been noted that results obtained using cyclic voltammetry are dependant on, among other factors, the measurement sweep rate. This indicates a lack of isolation between displacement and Faradaic mechanisms. Our measurements were repeated using wait-times of 4, 16, 32 and 64 seconds between voltage increments, allowing us to determine the effect of sweep rate. From these measurements and those of a separate investigation\footnote{We took measurements of the interface's response to voltage steps when left to settle for 10 000 seconds, of which the first 250\thinspace seconds are shown in figure~\ref{fig:CPE_currentVsTime}. Those measurements show a trend of decreasing current stabalisation time as the overpotential steps increase. Sixty four seconds after stepping from 0.64\thinspace V to 0.72\thinspace V, the current has stabalised to $95\%$ of its value at 10\,000 seconds. At overpotential steps for higher voltages, the settling time is further reduced. These measurements were made in still solution and we expect that stirring will reduce the time to equilibrium.} we concluded that a wait-time of 64 seconds was sufficient.
\begin{figure}
    \begin{center}
        \includegraphics{graphics/CPE_currentVsTime}
    \end{center}
    \caption{Current versus time after a stepped voltage increment across a pair of interfaces. Time before 64 seconds is highlighted in grey. Measurements were taken with a wait time of 10,000 seconds between increments.}
    \label{fig:CPE_currentVsTime}
\end{figure}

@@

11. P3 footnote. ``The response of the CPE'': this is confusing! Surely this is the response of a pair of electrodes? The CPE is an element of your model.\\
{\color{OliveGreen} 
    Item 30\\
    {\color{Red} This must form part of the inaccurate use of words comment. It's not right to say response of a pair of electrodes since there are other effects. Reword.}
    Removed reference to the CPE element and have better quantified the settling period in that footnote.
}\\
